Full Title of Article

### 2022-06-14 acml/acml22_paper.tex
fixed example 1

@@

\begin{enumerate}
\item One example to show that (a) variance and (b) standard error are
  good estimates to what extend to trust the ALE plot.
\item One example to show the importance of variable size bins
\end{enumerate}

\subsection{Real Data sets}

@@

%\acks{Acknowledgements should go at the end, before appendices and references. You can uncomment this for the camera-ready version on paper acceptance.}

>>>>

\usepackage{graphicx}
\graphicspath{{../examples/}}

@@

\subsubsection{Case 1}

One example to show that (a) variance and (b) standard error are good
estimates to what extend to trust the ALE plot. More specifically; (a)
the variance shows how far away from the ALE plot the global effect
can be and (b) the standard error shows how wrong the ALE plot can be.
Test to see how it changes with different sample size.

\begin{figure}[htp]
\begin{center}
  \includegraphics[width=0.3\textwidth]{example_1/im_1.png}
  \includegraphics[width=0.3\textwidth]{example_1/im_3.png}
  \includegraphics[width=0.3\textwidth]{example_1/im_5.png}\\
  \includegraphics[width=0.3\textwidth]{example_1/im_2.png}
  \includegraphics[width=0.3\textwidth]{example_1/im_4.png}
  \includegraphics[width=0.3\textwidth]{example_1/im_6.png}
\caption{A spiral.}\label{fig:edfd}
\end{center}
\end{figure}

\subsubsection{Case 2}

One example to show that (a) variance minimization is a good criterion
in case of linear feature and fixed-size feature effect and (b)
variable-size bins estimates as well as the best fixed-size.

\subsubsection{Case 3}

One example to show that variance minimization is a good criterion in
case of linear feature and variable-size feature effect. In this case,
variable-size bins estimates better than any possible fixed size.

\subsubsection{Case 4}

One example to show that (a) variance minimization is a good criterion
in case of non-linear feature effect. In this case, show that
variable-size bins estimates better than any possible fixed size.

\subsection{Real Dataset}

@@

% \acks{Acknowledgements should go at the end, before appendices and
% references. You can uncomment this for the camera-ready version on
% paper acceptance.}
